---
title: "TCGA PRS"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: flatly
---

```{r pre-setup, include=FALSE, eval=T}
knitr::opts_chunk$set(fig.width = 6, fig.height = 4, warning=F, message=F, comment=NA, fig.align = 'center')
```

```{r libraries, include=FALSE}
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
suppressMessages(library(ggsignif))
suppressMessages(library(gridExtra))
theme_set(theme_bw())
```

## Building PRS in TCGA Data

To build PRS, we use SNPs published in literature as discussed below. We use PRSice to compute the per-sample PRS.

Here, I focus on Breast Cancer PRS, because we can validate the outcome by comparing to non-BRCA tumor types.

I obtained a second set of 3820 SNPs from [Mavadatt et al](https://www.ncbi.nlm.nih.gov/pubmed/30554720) which were associated with BRCA. These SNPs were inferred via Lasso. From the paper: "the dataset used for development of the PRSs comprised 94,075 breast cancer-affected case subjects and 75,017 control subjects of European ancestry from 69 studies in the BCAC". As shown below, PRS is significantly higher in BRCA than in non-BRCA. This PRS is also better seperated from non-BRCA compared to the set of 77 SNPs above. 


```{r brca.prs}
brca.prs <- read.delim('../data/Lasso_PRS.profile', sep="", header=T)

brca.prs[brca.prs$FID=='TCGA-BRCA','type'] = 'BRCA'
brca.prs[brca.prs$FID!='TCGA-BRCA','type'] = 'Other'

p1 <- ggplot(brca.prs, aes(x=type,y=SCORE, color=type)) + geom_boxplot() + 
  xlab('Tumor Type') + ylab(expression(PRS)) + 
  geom_signif(comparisons = list(c("BRCA", "Other")),
              map_signif_level=TRUE, color='black',tip_length = 0.1, y_position = 3e-4, test = 't.test') +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size=16), legend.position = 'none')

p2 <- ggplot(brca.prs, aes(x=SCORE, fill=type)) + geom_density(alpha=0.2) + 
  xlab(expression(PRS)) + ylab('Frequency') + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size=16), legend.position = 'none')

grid.arrange(p1, p2, ncol=2, top='77 Published SNPs')
```

